---
title: "Instruction template to connect Rmd to Rspace"
author: "Hanneke Leegwater"
date: "`r Sys.Date()`"
output:   
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
    df_print: kable
knit: (function(inputFile, encoding) { rmarkdown::render(inputFile, encoding = encoding, output_file = stringr::str_replace(inputFile, ".Rmd",paste0("_", stringr::str_remove_all(Sys.Date(),"-"),'.html'))) })
---

# Template instructions

This is an Rmd file that has similar headings to the template used in Rspace. As long as you keep main headings (everything with a single \#) the same as in this template, you can play as much as you want with other heading levels (##, \###). You can use the Rspace API to upload the knitted report to Rspace.

Be aware that that template has even more sections, but you have to fill those in yourself, like the path to your code, or external instructions.

**DO:**

-   Check if the version number in this document is the same as the most recent template you should use.
-   Code things like usual
-   Knit the file to a html report.

**DONT:**

-   Change the headings with one \# or add more main headings!!!!! Consult the data steward if you do not like the headings, because these are the DDS2 standards and we have to keep standards.

# Assay Template Used

DDS Beltman - In Silico Experiment v0.1.1

# Description or Purpose

For example the following sub-headers

## Background

## Data sources

## Analysis plan

# Results

I like numbering sections, but you do you.

## 0. Preparations

### Load R libraries

```{r}
library(tidyverse)
library(here)
library(mixOmics)
library(pheatmap)
library(cowplot)
```

### Set input and output directories

Show base path to the project that is used in the analysis.

Pro tip: The here package is awesome to use relative paths within an R project.

```{r}
here()
```

Set input data directory.

```{r}
data_dir <- here("data")
str_glue("Using data from {data_dir}")
#stopifnot(dir.exists(data_dir))
```

Set output data directory and create if it does not exist. This is an example to get the date in the output folder

```{r}
datestamp <- str_remove_all(Sys.Date(), "-")
output_dir <- here("results", str_glue("{datestamp}_output"))
str_glue("Output directory path is {output_dir}")
#stopifnot(dir.exists(output_dir))
```

### Define functions

I like having my in-script functions all together.

## 1. Load data

## 2. More stuff

# Conclusion

I like writing down conclusions here

## Doubts and limitations

And then my doubts or things I forgot here.

## Future assays

And a to do list